MSGenova (Clean version) Rmakrdown Report

### 2022-09-13 script/ms_report.Rmd
correct fogotten config, add yaml library to report

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_library, echo=FALSE, warning=FALSE, error=FALSE}
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
vector_calling<-params$vector
run_chromomap<-FALSE
DP.min<-params$DP.min
AR.min<-params$AR.min
workspace<-params$result_dir
sample_sheet<-params$sample
trimmo<- params$trimmo
flagstat<- params$flagstat
haplotype_caller<- params$haplotype_caller
setwd(workspace)
```

@@

read_file<-function(pathway){
#sample<-list.files(getwd())
#vector<-list.files(list.files(getwd())[1])
sample<-list.files(pathway)
vector<-list.files(paste0(pathway,"/",sample[1]))
i=0
for (spl in sample){
  for (v in vector){
    table<-read.table(paste0(pathway,"/",spl,"/",v,"/5.",v,"_insertion.annotated.bed"),header = FALSE,col.names = c("Chr","Breakpoint","SuppRead","TDNA_info","Orientation","Freq","Annotation"))
    if(! nrow(table)==0){
      #add sample and vector columns
      table["sample"]<-spl
      table["vector"]<- v
      if(i==0){
        final_table<-table
        i=i+1
      }else{
        final_table<-rbind(table,final_table)
      }
      i=i+1
    }
  }
}
return(final_table)
}
```

@@

```{r define_variable}
#sample<-list.files(getwd())
#vector<-list.files(list.files(getwd())[1])
pathway=paste0(workspace,"/05_tdnascan/")
sample<-list.files(pathway)
vector<-list.files(paste0(pathway,"/",sample[1]))
# read sample file
sample_sheet<-read.table(sample_sheet,sep="\t",header=TRUE)
```

>>>>

```{r setup, include=FALSE}
workspace<-params$result_dir
knitr::opts_chunk$set(echo = TRUE,root.dir=workspace)
```

```{r load_library, echo=FALSE, warning=FALSE, error=FALSE}
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
library(yaml)
vector_calling<-params$vector
run_chromomap<-FALSE

DP.min<-params$DP.min
AR.min<-params$AR.min
#workspace<-params$result_dir

sheet<-params$sample
trimmo<- params$trimmo
flagstat<- params$flagstat
haplotype_caller<- params$haplotype_caller
#setwd(workspace)
```

@@

read_file<-function(pathway){
sample<-list.files(pathway)
vector<-list.files(paste0(pathway,"/",sample[1]))
i=0
for (spl in sample){
  for (v in vector){
    table<-read.table(paste0(pathway,"/",spl,"/",v,"/5.",v,"_insertion.annotated.bed"),header = FALSE,col.names = c("Chr","Breakpoint","SuppRead","TDNA_info","Orientation","Freq","Annotation"))
    if(! nrow(table)==0){
      #add sample and vector columns
      table["sample"]<-spl
      table["vector"]<- v
      if(i==0){
        final_table<-table
        i=i+1
      }else{
        final_table<-rbind(table,final_table)
      }
      i=i+1
    }
  }
}
return(final_table)
}
```

@@

```{r define_variable}
pathway=paste0(workspace,"/05_tdnascan/")
sample<-list.files(pathway)
print(sample)
vector<-list.files(paste0(pathway,"/",sample[1]))
print(vector)
# read sample file
sample_sheet<-read.table(paste0(workspace,"/genome/sample_sheet"),sep="\t",header=TRUE)
```
